---  
title: "scRNA-seq: Annotation Mini Report"
author: "SysBioLab"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    fig_width: 12
---

<!-- Sergio Alías, 20231123 -->
<!-- Last modified 20231123 -->

<style type='text/css'>
    body .main-container {
        max-width: 90%;

    }

    .plot_real_size {
      overflow: scroll;
      max-height: 600px;
    }

    .plot_real_size img{
      max-width: none;
      max-height: none;
    }

    embed {
   
  }   
</style>

<style>
.dropdown-content {
  display: none;
}

.dropdown:hover .dropdown-content {
  display: block;
}
</style>

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }


</style>


## Dotplots for cell type annotation: WT


```{r, echo = FALSE, results = "asis"}

colGEX <- c("grey85", brewer.pal(7, "Reds"))

data_gen <- read.table("markers-general", header = FALSE, sep = "\t", stringsAsFactors = FALSE)
marker_list_gen <- vector("list", length = nrow(data_gen))
for (i in 1:nrow(data_gen)) {
  words <- unlist(strsplit(as.character(data_gen[i, 2]), ","))
  marker_list_gen[[i]] <- words
  names(marker_list_gen)[i] <- as.character(data_gen[i, 1])
}
data_spe <- read.table("markers-specific", header = FALSE, sep = "\t", stringsAsFactors = FALSE)
marker_list_spe <- vector("list", length = nrow(data_spe))
for (i in 1:nrow(data_spe)) {
  words <- unlist(strsplit(as.character(data_spe[i, 2]), ","))
  marker_list_spe[[i]] <- words
  names(marker_list_spe)[i] <- as.character(data_spe[i, 1])
}

```

```{r, echo=FALSE, message=FALSE, results="asis", out.width="100%"} 

for (element_name in names(marker_list_gen)) {
  
  cat(paste0("\n\n### General markers: ", element_name, "\n\n"))
  
  print(DotPlot_scCustom(seu.WT,
                   features = marker_list_gen[[element_name]],
                   flip_axes = TRUE,
                   colors_use =  colGEX))
  cat("  \n")
}

```

```{r, echo=FALSE, message=FALSE, results="asis", out.width="100%"} 

for (element_name in names(marker_list_spe)) {
  
  cat(paste0("\n\n### Specific markers: ", element_name, "\n\n"))
  
  print(DotPlot_scCustom(seu.WT,
                   features = marker_list_spe[[element_name]],
                   flip_axes = TRUE,
                   colors_use =  colGEX))
  cat("  \n")
}

```

## Dotplots for cell type annotation: mutant

```{r, echo=FALSE, message=FALSE, results="asis", out.width="100%"} 

for (element_name in names(marker_list_gen)) {
  
  cat(paste0("\n\n### General markers: ", element_name, "\n\n"))
  
  print(DotPlot_scCustom(seu.mutant,
                   features = marker_list_gen[[element_name]],
                   flip_axes = TRUE,
                   colors_use =  colGEX))
  cat("  \n")
}

```

```{r, echo=FALSE, message=FALSE, results="asis", out.width="100%"} 

for (element_name in names(marker_list_spe)) {
  
  cat(paste0("\n\n### Specific markers: ", element_name, "\n\n"))
  
  print(DotPlot_scCustom(seu.mutant,
                   features = marker_list_spe[[element_name]],
                   flip_axes = TRUE,
                   colors_use =  colGEX))
  cat("  \n")
}

```

## Dotplots for cell type annotation: time 48


```{r, echo=FALSE, message=FALSE, results="asis", out.width="100%"} 

for (element_name in names(marker_list_gen)) {
  
  cat(paste0("\n\n### General markers: ", element_name, "\n\n"))
  
  print(DotPlot_scCustom(seu.48,
                   features = marker_list_gen[[element_name]],
                   flip_axes = TRUE,
                   colors_use =  colGEX))
  cat("  \n")
}

```

```{r, echo=FALSE, message=FALSE, results="asis", out.width="100%"} 

for (element_name in names(marker_list_spe)) {
  
  cat(paste0("\n\n### Specific markers: ", element_name, "\n\n"))
  
  print(DotPlot_scCustom(seu.WT,
                   features = marker_list_spe[[element_name]],
                   flip_axes = TRUE,
                   colors_use =  colGEX))
  cat("  \n")
}

```

## Dotplots for cell type annotation: time 62

```{r, echo=FALSE, message=FALSE, results="asis", out.width="100%"} 

for (element_name in names(marker_list_gen)) {
  
  cat(paste0("\n\n### General markers: ", element_name, "\n\n"))
  
  print(DotPlot_scCustom(seu.62,
                   features = marker_list_gen[[element_name]],
                   flip_axes = TRUE,
                   colors_use =  colGEX))
  cat("  \n")
}

```

```{r, echo=FALSE, message=FALSE, results="asis", out.width="100%"} 

for (element_name in names(marker_list_spe)) {
  
  cat(paste0("\n\n### Specific markers: ", element_name, "\n\n"))
  
  print(DotPlot_scCustom(seu.62,
                   features = marker_list_spe[[element_name]],
                   flip_axes = TRUE,
                   colors_use =  colGEX))
  cat("  \n")
}

```