---  
title: "scRNA-seq: Integration Mini Report"
author: "SysBioLab"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    fig_width: 12
---

<!-- Sergio Alías, 20231031 -->
<!-- Last modified 20231216 -->

<style type='text/css'>
    body .main-container {
        max-width: 90%;

    }

    .plot_real_size {
      overflow: scroll;
      max-height: 600px;
    }

    .plot_real_size img{
      max-width: none;
      max-height: none;
    }

    embed {
   
  }   
</style>

<style>
.dropdown-content {
  display: none;
}

.dropdown:hover .dropdown-content {
  display: block;
}
</style>

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }


</style>

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# Integrating by time: 48 vs 62

```{r setup, include = FALSE}
library(Seurat)
library(dplyr)
library(gridExtra)
library(RColorBrewer)
library(ggplot2)
library(scCustomize)
setwd("outs")
seu.markers.48 <- readRDS("seu.markers.48.RDS")
seu.markers.62 <- readRDS("seu.markers.62.RDS")
seu.48 <- readRDS("seu.48.RDS")
seu.62 <- readRDS("seu.62.RDS")
```

## UMAP: 48 vs 62

<div class="superbigimage">

```{r c10, echo = FALSE, results = "asis"}
DimPlot(seu.48, reduction = "umap", label = FALSE) + guides(color = guide_legend(override.aes = list(size=4), ncol=1))
```

</div>
<div class="superbigimage">

```{r c10b, echo = FALSE, results = "asis"}
DimPlot(seu.62, reduction = "umap", label = FALSE) + guides(color = guide_legend(override.aes = list(size=4), ncol=1))
```
</div>

## UMAP splitted by genotype: 48 vs 62

<div class="superbigimage">

```{r c20, echo = FALSE, results = "asis"}
DimPlot(seu.48, reduction = "umap", split.by = "genotype") + guides(color = guide_legend(override.aes = list(size=4), ncol=1))
```
</div>
<div class="superbigimage">

```{r c20b, echo = FALSE, results = "asis"}
DimPlot(seu.62, reduction = "umap", split.by = "genotype") + guides(color = guide_legend(override.aes = list(size=4), ncol=1))
```

</div>

## UMAP grouped by genotype: 48 vs 62

```{r c30, echo = FALSE, results = "asis"}
DimPlot(seu.48, reduction = "umap", group.by = "genotype")
```

```{r c30b, echo = FALSE, results = "asis"}
DimPlot(seu.62, reduction = "umap", group.by = "genotype")
```


## PCA

## PCA: 48 vs 62

<div class="superbigimage">

```{r pc10, echo = FALSE, results = "asis"}
DimPlot(seu.48, reduction = "pca", label = FALSE) + guides(color = guide_legend(override.aes = list(size=4), ncol=1))
```

</div>
<div class="superbigimage">

```{r pc10b, echo = FALSE, results = "asis"}
DimPlot(seu.62, reduction = "pca", label = FALSE) + guides(color = guide_legend(override.aes = list(size=4), ncol=1))
```
</div>

## PCA splitted by genotype: 48 vs 62

<div class="superbigimage">

```{r pc20, echo = FALSE, results = "asis"}
DimPlot(seu.48, reduction = "pca", split.by = "genotype") + guides(color = guide_legend(override.aes = list(size=4), ncol=1))
```
</div>
<div class="superbigimage">

```{r pc20b, echo = FALSE, results = "asis"}
DimPlot(seu.62, reduction = "pca", split.by = "genotype") + guides(color = guide_legend(override.aes = list(size=4), ncol=1))
```

</div>


## PCA grouped by genotype: 48 vs 62

```{r pc30, echo = FALSE, results = "asis"}
DimPlot(seu.48, reduction = "pca", group.by = "genotype")
```

```{r pc30b, echo = FALSE, results = "asis"}
DimPlot(seu.62, reduction = "pca", group.by = "genotype")
```


## Markers 48

### Top 10 markers

```{r c40, echo = FALSE, results = "asis"}
grid.table(slice_max(seu.markers.48, n = 10, order_by = avg_log2FC))
```

### Canonical markers

```{r ccc0, echo = FALSE, results = "asis"}
can.mark <- c("STMN2",
              "GAP43",
              "DCX",
              "VIM", 
              "HES1", 
              "SOX2", 
              "TBR1", 
              "GAD1", 
              "GAD2", 
              "vGLUT1", 
              "vGAT", 
              "MYL1", 
              "MYH3", 
              "OLIG1/2", 
              "GFAP", 
              "SLC1A4", 
              "S100B", 
              "SLC17A7", 
              "SLC17A6", 
              "SLC32A1")
```

```{r cc40, echo = FALSE, results = "asis"}
grid.table(seu.markers.48[can.mark,][complete.cases(seu.markers.48[can.mark,]),])
```

## Markers 62

### Top 10 markers

```{r c50, echo = FALSE, results = "asis"}
grid.table(slice_max(seu.markers.62, n = 10, order_by = avg_log2FC))
```

### Canonical markers

```{r cc50, echo = FALSE, results = "asis"}
grid.table(seu.markers.62[can.mark,][complete.cases(seu.markers.62[can.mark,]),])
```

## Markers expression: 48 vs 62

### Top 10 markers

```{r c60, echo = FALSE, results = "asis", fig.show="hold", out.width="50%", fig.height = 25}
Stacked_VlnPlot(seu.48,
        ncol = 1,
        features = slice_max(seu.markers.48, n = 10, order_by = avg_log2FC)$gene,
        pt.size = 0,
        x_lab_rotate = 90)
Stacked_VlnPlot(seu.62,
        ncol = 1,
        features = slice_max(seu.markers.62, n = 10, order_by = avg_log2FC)$gene,
        pt.size = 0,
        x_lab_rotate = 90)
```

### Canonical markers

```{r cc60, echo = FALSE, results = "asis", fig.show="hold", out.width="50%", fig.height = 25}
Stacked_VlnPlot(seu.48,
        ncol = 1,
        features = seu.markers.48[can.mark,][complete.cases(seu.markers.48[can.mark,]),]$gene,
        pt.size = 0,
        x_lab_rotate = 90)
Stacked_VlnPlot(seu.62,
        ncol = 1,
        features = seu.markers.62[can.mark,][complete.cases(seu.markers.62[can.mark,]),]$gene,
        pt.size = 0,
        x_lab_rotate = 90)
```

## Canonical markers expression patterns

### 48

```{r cc70, echo = FALSE, results = "asis", warning = FALSE, out.width = "100%", fig.height = 20}
colGEX <- c("grey85", brewer.pal(7, "Reds"))
plotTheme <- theme_classic(base_size = 18)

FeaturePlot_scCustom(seu.48, reduction = "umap", pt.size = 0.1, num_columns = 3,
                  features = seu.markers.48[can.mark,][complete.cases(seu.markers.48[can.mark,]),]$gene, order = TRUE) &
  scale_color_gradientn(colors = colGEX) & plotTheme & coord_fixed()
```

### 62

```{r cc80, echo = FALSE, results = "asis", warning = FALSE, out.width = "100%", fig.height = 20}

FeaturePlot_scCustom(seu.62, reduction = "umap", pt.size = 0.1, num_columns = 3,
                  features = seu.markers.62[can.mark,][complete.cases(seu.markers.62[can.mark,]),]$gene, order = TRUE) &
  scale_color_gradientn(colors = colGEX) & plotTheme & coord_fixed()
```